\chapter{Evaluation}
\label{chap:discussion}
%The SAD course resulted in a through analysis and design instead of spending time learning how the ASP.NET MVC 2 framework works.
We use the SAD course to make a thorough analysis and design.
We do however design our application prior to choosing our framework to build it upon -- namely the ASP.NET MVC 2 framework.
This means that a lot of the time initially spent on the design is completely wasted as the original design can not be implemented properly using the framework.
Therefore the implementation is commenced late in the process which result in lack of the required time to throughly make a full application test and correct all bugs.
This can be avoided by achieving knowledge of the framework prior to the design phase. 
In general we use a lot of new technologies which we have a very sparse knowledge of. This results in parts of the application where it can been done more comprehensible and efficient.
%The whole learning process of this project is trial and error. 
When applying new technologies it can go well or you learn something 
If we have to start over, we will be able to save a great deal of time and start programming sooner, as we have experience with the \ooad{} method and how to use it to develop an application. Furthermore we have the technical platforms more in mind as this to some extent slows down the process as technical issues is encountered.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Udem\ae{}rket afsnit, men synes mere det er en diskusion af vores process -- i.e. evaluering -- end en diskusion
%af vores produkt, hvilket jeg mener ``Discussion'' burder indeholde.
%Vi kan evt. ændre det til ``Evaluation''? -- Done!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%