\documentclass{article}
\begin{document}
\section{What should we do}

\begin{itemize}
	\item It should be a general tool, not necessarily only university
	
	\begin{itemize}
		\item Use university as example only
		\item Use our own issues
	\end{itemize}
	
	\item General system, for a specific case - university
	\item A problem must be assigned to department
	\item Track the ID to see what have been done.
	\item Supervisor - head of technicians
	
	\begin{itemize}
		\item Able to what long the different techs use to solve problems
	\end{itemize}
	
	\item Use key words
	\item Based on key words the problems should be categorized and perhaps prioritized
	\item Estimation on each problem based on previous problems.
	\item Practical problems can be store multiple problems
	\item When a problem is posted, the system should suggest a solution if a similar problem has already been solved.
	\item Everything should be recorded
	
\end{itemize}

\section{PE}

\begin{itemize}
	\item SAD and OOP
	\item No exam in SAD we're almost sure
	\item Everything from SAD should be included, the actual project is not important
\end{itemize}

\section{How far are we -- what should we change}

\begin{itemize}
	\item Structure
	
	\begin{itemize}
		\item The system should assign the problems not only to department but also staff
		\item This assignment should be based on key words.
		\item Staffs work load should be include in the assignment of problems
		\item Key words should be chosen from a selection, so the poster needs to do it
		
		\begin{itemize}
			\item Include a ``Other category''-ish
		\end{itemize}
		
		\item We will have to chose from different paths
		
		\begin{itemize}
			\item Document this!!
			\item Which paths there are, which we chose and why.
		\end{itemize}
		
		\item We need to know have the user is notified when his problem is solved.
		\item Who will set priority
		\item Based on the category the priority could be set.
		\item there should be both estimation and a deadline
		
		\begin{itemize}
			\item Perhaps the deadline should also be based on previous problems
		\end{itemize}
		
		\item User to Client perhaps?
	\end{itemize}
	
\end{itemize}

\section{Other meeting}

\begin{itemize}
	\item Things should be sent 48 hours before meeting
	\item Later it should be 4-5 days before
	\item We sent an e-mail about next meeting
	\item Maybe the 6
	\item Should we change from Google code
	
	\begin{itemize}
		\item Perhaps change to university?
	\end{itemize}
	
\end{itemize}

\end{document}