\chapter{Evaluation}
\label{chap:discussion}
%The SAD course resulted in a through analysis and design instead of spending time learning how the ASP.NET MVC 2 framework works.
We have used the SAD course to make a thorough analysis and design.
We did however design our application prior to choosing our framework to build it upon -- namely the ASP.NET MVC 2 framework.
This means that a lot of the time we initially spent on the design was completely wasted as we realized that it could not be implemented properly using the framework.
Therefore we started very late on the implementation and did not use the required time to throughly make a full system test and correct all bugs.
This could be avoided by achieving knowledge of the framework prior to the design phase. 
In general we used a lot of new technologies which we had a very sparse knowledge of and this resulted in parts of the application where we afterwards can see that it could have been done more comprehensible and efficient.
The whole learning process of this project has been trial and error.
We tried applying new technologies and sometimes it went well or if not we learned something from it.

If we were to start over, we would now be able to save a great deal of time and get started programming sooner, as we now have experience with the \ooad{} method and how we would use it to develop an application. Furthermore would we have the technical platforms more in mind as this also to some extent slowed us down as we had some technical issues.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Udem\ae{}rket afsnit, men synes mere det er en diskusion af vores process -- i.e. evaluering -- end en diskusion
%af vores produkt, hvilket jeg mener ``Discussion'' burder indeholde.
%Vi kan evt. ændre det til ``Evaluation''? -- Done!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%