\section{Distribute Problems}
\label{sec:dispro}
Whenever a new problem is added it needs to be distributed to the staff member in the correct department with the lowest workload. 
The correct department is found by looking through all the tags of the problem and choosing the department that the most tags belong to.

There are two special cases which requires some attention. 
The case where two or more departments are equally represented in a problem and the case where a problem has no tags. 
In the first case a department is simply chosen by the order in which the department is in the unsorted list of possible departments. 
In the second case the staff member with the lowest workload will get the problem, no matter what department he/she belongs to.
If a problem is assigned to an inappropriate department we assume that any staff member would have the acquired knowledge to reassign the problem to the appropriate department. 


\begin{lstlisting}[style=sourceCode, caption=\myCaption{The overloads for the \me{GetStaff} method}, label=lst:getstaffoverloads,float=h]
public static IPerson GetStaff(Problem Problem, List<Person> PersonSet)
{
    var persons = new List<IPerson>();
    foreach (var item in PersonSet)
    {
        persons.Add(item);
    }
    return GetStaff(Problem, persons, GetDepartment(Problem.Tags));
}

public static IPerson GetStaff(Problem Problem, List<IPerson> PersonSet)
{
    return GetStaff(Problem, PersonSet, GetDepartment(Problem.Tags));
}

public static IPerson GetStaff(Problem Problem, List<Person> PersonSet, Department department)
{
    var persons = new List<IPerson>();
    foreach (var item in PersonSet)
    {
        persons.Add(item);
    }
    return GetStaff(Problem, persons, department);
}

public static IPerson GetStaff(Problem Problem, Department department)
{
    return GetStaff(Problem, department.Persons.ToList(), department);
}
\end{lstlisting}
The method that does the actual work is the \me{GetStaff} method which has several overloads. The overloads can be seen in code snippet \ref{lst:getstaffoverloads}. The actual method can be seen in code snippet \ref{lst:getstaff}. 
All overloads takes a \cl{Problem} as parameter. 
The other takes either a department or a list of \cl{IPerson}, which is a \cl{Person} interface made to make it more testable. 
Some overloads use both parameters.

\begin{lstlisting}[style=sourceCode, caption=\myCaption{the \me{GetStaff} method}, label=lst:getstaff,float=hp]
public static IPerson GetStaff(Problem Problem,  List<IPerson> PersonSet, Department department)
{ 
    IEnumerable<IPerson> persons = null;
    if (department != null)
    {
         persons = PersonSet.Where(x => x.Department == department && x.IsStaff() == true);
         if (persons == null || persons.Count() == 0)
         {
             persons = PersonSet.Where(x => x.IsStaff() == true);
         }
    } else {
         persons = PersonSet.Where(x => x.IsStaff() == true);
    }
    Double min = Double.MaxValue;
    if (persons.Count() == 0 || persons == null)
    {
        throw new ArgumentNullException("The Person List were empty");
    }
    IPerson staff = persons.First();
    foreach (var person in persons)
    {
            var workload = person.GetWorkload();
            if (workload < min)
            {
                min = workload;
                staff = person;
            }   
    }
    if (persons == null)
    {
        staff = persons.First();
    }
   
    return staff;
}
\end{lstlisting}