\section{Software}
\label{sec:software}

Our system relies on two things:

\begin{itemize}
	\item Database
	\item Web server
\end{itemize}

These two are described in following subsections.

\subsection{DBMS}
\label{subsec:dbms}

Using an external DBMS allows it to be installed across multiple machines instead on a single computer. This is a good thing as it makes our system more portable, allowing it to be either installed on a single computer, or more computers.

The differences which we have considered between these two DBMS's are listed in figure \ref{fig:DBMS}\cite{postgres08}

\begin{figure}[htb]
	\centering
	\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
		\begin{tabularx}{\textwidth}{L|L|L}
			\textbf{Feature}&\textbf{PostgreSQL}&\textbf{Microsoft SQL Server} \\
			\hline
			Accessible&BSD Open source&Requires license, but we do have this through the university. \\ 
			Cooperative with our tools&Hard to incorporate into Visual Studio 2010. & Easy to incorporate into Visual studio 2010. \\ 
			Experience in our work group&We have had a course based on PostgreSQL. & None, but resembles other SQL DBMS's. \\ 
		\end{tabularx}
	\morscaption{DBMS's compared}
	\label{fig:DBMS}
\end{figure}

The \hdesk requires a DBMS supporting the query language \sql[] and relational database model\cite{Sudershan2011}.
We have chosen Microsoft SQL Server version 10.50.1600.1 in favor of \posgresql[], which we have past experience with due to a university course.
However \posgresql[] is less integrated with Visual Studio 2010, which we are using for developing our system.

\subsection{Web Server}
\label{subsec:webserver}

%The required software for our system consists of two major applications; a DBMS supporting the query language \sql[], and a web server capable of running our web-scripting interface of choice. 
%The data storage model will be the relational database model and the DBMS we will be using is \posgresql[] version 8.4.5 as our only DBMS. \fixme{Ret s\aa snar vi ved hvad pokker vi vil bruge}

We have chosen to implement our system as a webapplication, as it minimizes the amount of software which the users of our system has to install before using our system.
The language of choice will be C\# using the ASP.NET MVC2(Model-View-Controller) framework, therefore should the webserver support this.

We could have used other web-frameworks, but chose ASP.NET MVC2 because we could use Visual Studio 2010 and C\# which we have all used during a course in object oriented programing.

We also discussed not using a framework at all, and simply build everything from ground.
We chose not do this because we assessed it is best to use what is already available, further more the framework has been developed for a long time and is therefore likely to be more effective and secure than what we could make within in this limited timeframe.


\subsection{Operating System}
\label{subsec:operating_system}
It is a quite natural decision to choose a operating system from Microsoft, as we have chosen a Windows based programming language, C\#. See section \ref{sec:design_language} for more.
We are using Microsoft Windows server 2008 R2 Enterprise. 