\section{System Definition}
\label{sec:factor}
\label{sec:systemdefinition}
In order to define our system we use the FACTOR criterion\cite[p.~39]{roedeaalborg}. These criteria contains different parts of the requirements, and it will help us derive the system definition.  \\
\ \\
{\Large \textbf{F}}unctionality \\
Our application contain features aimed at easing the problem-solving process for service employees, therefore the application needs to have the following features:
\begin{itemize}
\item Problem distribution\\
The application should distribute problems to the relevant service department and balance the workload of service employees so all have a equal workload. 
\item Problem categorization \\
Categorize problem and thereby making it easy to find relevant problems.
\item Ranking of problems \\
Unsolved Problems are displayed on a ranked list, depending on their importance.
\item Keep track \\
The application should be able to keep track of all the information regarding a problem, this being
\begin{itemize}
	\item When it approximately will be solved
	\item Who is assigned to solve the problem
	\item What the deadline is, and if it is exceeded
	\item What tags and categories are related to the problem 
	\item Comments related to the problem
\end{itemize}
\item Knowledge saved \\
The application should be able to recognize common problems and recommend similar problem to the user, and by that saving the service employee the bother of solving common problems. 
\item Statistics \\
Allow the supervisor to monitor the work process of the employees.
\end{itemize}
\ \\
{\Large \textbf{A}}pplication domain \\
This application is applicable to office environments which deals with solving of problems.\\
\ \\
{\Large \textbf{C}}onditions \\ 
The end users are not required to have any expert level knowledge to use the application. The service personal have to learn to use the staff interface to solve problems. The administrators have to learn to use the functionality in the administrator interface.   \\
\ \\
{\Large \textbf{T}}echnology \\
In the development of our program we use C\# along with the Model-View-Controller framework 2 that exists within ASP.NET framework. We use a server and use AnhkSVN and Microsoft SQL server along with visual studio 2010.\\
\\
The end result is a web interface running on a webserver, with underlying SQL database.\\
\ \\
{\Large \textbf{O}}bjects \\
Problems, solution, \aclient[]s, \astaff[] members, \admin{}s, departments, categories and tags. \\
\ \\
{\Large \textbf{R}}esponsibility \\
Our application is responsible for keeping track of all problems within the physical environment of an organization. It is also responsible for distributing tasks amongst employees and supplying statistics about the progress to their supervisors. Finally it is also responsible for enabling users and technical employees to communicate about a problem and the following solution.
\ \\ 

%%% Nutid
Using these FACTOR criteria the following system definition is derived:
\begin{itemize}
\item The application is be web-based so that we can create an application capable of running without prior installation.
\item The application contains prioritized tags, enabling us to determine the importance of problems
\item The application keeps track of the estimated completion time of the problem along with comments and what employee is responsible for solving the problem. This enables us to create statistic about problem solving efficiency and individual employees.
\item The application is able to save and suggest prior problems and their solutions to users.
\item The application takes into account, the workload of the employees to estimate how long a problem will take to solve.
\item The application contains nothing but dynamic data within the problem domain, so that the application can run in different environments.
\item The application contains a structure that can handle problems, departments, categories, tags, employees, supervisors and ordinary users.
\end{itemize}


%% Fremtid
\begin{comment}
Using these FACTOR criteria, we arrive at the following system definition:
\begin{itemize}
\item The application is be web-based so that we can create an application capable of running without prior installation.
\item The application should contain prioritized tags, enabling us to determine the importance of problems
\item The application should keep track of the estimated completion time of the problem along with comments and what employee is responsible for the problem. This will enable us to create statistic about problem solving efficiency and individual employees.
\item The application should be able to save and suggest prior problems and their solutions to users.
\item The application should take into account, the workload of the employees to estimate how long a problem will take to solve.
\item The application should should contain nothing but dynamic data within the problem domain, so that the application can run in different environments.
\item The application should contain a structure that can handle problems, departments, categories, tags, employees, supervisors and ordinary users.
\end{itemize}
\end{comment}


